Analytical Predictions of Explanet Obliquities Generated by Planet-Disk Interactions

### 2020-02-20 writeups/Su_weak_tides.tex
stash dong feedback on weak tCS draft

    \documentclass[
        fleqn,
        usenatbib,
        referee,
    ]{mnras}
    \usepackage{
        amsmath,
        amssymb,
        newtxtext,
        newtxmath,
        graphicx,
        ae, aecompl,
        booktabs,
        caption,
        subcaption,
    }
    \usepackage[T1]{fontenc}
    \captionsetup{compatibility=false}

@@

Generally, these EOM have equilibria at the points that are both a CS and
satisfy $\dot{s} = 0$ under weak tidal friction. These are stable as $\epsilon
\to 0$, see Appendix~\ref{app:cs_stab}. On Fig.~\ref{fig:quiver}, these are the
intersection of the locations of CS1 and CS2 with the line $\dot{s} = 0$. It is
clear that the locations of these equilibria depend on the value of $s_c$. Call
these generalized equilibria \emph{tidal Cassini States} (tCS), and number them
tCS1 and tCS2 depending on whether they are CS1 or CS2 states. Shown
\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/6equils0_06.png}
    \caption{Location of tCS\@. Vertical line is spin rate below which tCS is
    destroyed.}\label{fig:6equils}
\end{figure}

Furthermore, if tides are too strong (large $\epsilon$), tCS2 can become
unstable (cite Fabrycky). The required $\epsilon$ for stability of tCS2 is given
by
\begin{equation}
    \epsilon \leq \frac{\eta_2 \sin I}{1 - \mu_2^2},
\end{equation}
where $\eta_2$ and $\mu_2$ are evaluated at tCS2.

@@

As a result of \autoref{ss:tidal_eqs}, the tCS are the only possible final
outcomes. We generate initial spin vectors $\hat{s}$ for isotropic initial
distribution $\p{\cos \theta, \phi}$, and marginalize over $\phi$ (which
generally cannot be fixed by any formation mechanism) in histograms. This gives
histograms in Figs.~\ref{fig:Hhists_0_06,fig:Hhists_0_20,fig:Hhists_0_70}
\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5Hhists0_06_5.png}
    \caption{$s_c = 0.06$. Note that it is difficult to reach
    tCS2.}\label{fig:Hhists_0_06}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5Hhists0_20_5.png}
    \caption{$s_c = 0.2$. Note that tCS2 is both reached with substantial
    probability and has substantial obliquity.}\label{fig:Hhists_0_20}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5Hhists0_60_5.png}
    \caption{$s_c = 0.6$. Note that tCS2 becomes attracting over tCS1, but will
    have obliquity $\approx I$ and is uninteresting.}\label{fig:Hhists_0_70}
\end{figure}

@@

Assuming that $\hat{s}$ is drawn from an isotropic distribution, we may then
calculate the probabilities of going to either tCS as a function of $s_c$. This
is shown below for $I = 5^\circ$
\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5probs_5.png}
    \caption{Top: total probability of ending up in tCS2 (blue dots) and the
    prediction ignoring separatrix capture (red line). Bottom:
    obliquities of the tCSs.}\label{fig:probs}
\end{figure}

Note that while only the results for an isotropic distribution of initial
$\hat{s}$ are shown, in principle arbitrary distributions $P\p{\theta_i}$ can be
convolved against the $P_{tCS2}\p{\theta_i}$ distributions shown in
\autoref{ss:q_dist}.

>>>>

% label C_\pm on fig 2
% unify 3 & 4, choose consistent q/cos q
    \documentclass[
        fleqn,
        usenatbib,
        referee,
    ]{mnras}
    \usepackage{
        amsmath,
        amssymb,
        newtxtext,
        newtxmath,
        graphicx,
        ae, aecompl,
        booktabs,
        caption,
        subcaption,
    }
    \usepackage[T1]{fontenc}
    \captionsetup{compatibility=false}

@@

Generally, these EOM have equilibria at the points that are both a CS and
satisfy $\dot{s} = 0$ under weak tidal friction. These are stable as $\epsilon
\to 0$, see Appendix~\ref{app:cs_stab}. On Fig.~\ref{fig:quiver}, these are the
intersection of the locations of CS1 and CS2 with the line $\dot{s} = 0$. It is
clear that the locations of these equilibria depend on the value of $s_c$. Call
these generalized equilibria \emph{tidal Cassini Equilibria} (tCE), and number
them tCE1 and tCE2 depending on whether they are CS1 or CS2 states. Shown
\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/6equils0_06.png}
    \caption{Location of tCE\@. Vertical line is spin rate below which tCE is
    destroyed.}\label{fig:6equils}
\end{figure}

Furthermore, if tides are too strong (large $\epsilon$), tCE2 can become
unstable (cite Fabrycky). The required $\epsilon$ for stability of tCE2 is given
by
\begin{equation}
    \epsilon \leq \frac{\eta_2 \sin I}{1 - \mu_2^2},
\end{equation}
where $\eta_2$ and $\mu_2$ are evaluated at tCE2.

@@

As a result of \autoref{ss:tidal_eqs}, the tCE are the only possible final
outcomes. We generate initial spin vectors $\hat{s}$ for isotropic initial
distribution $\p{\cos \theta, \phi}$, and marginalize over $\phi$ (which
generally cannot be fixed by any formation mechanism) in histograms. This gives
histograms in Figs.~\ref{fig:Hhists_0_06,fig:Hhists_0_20,fig:Hhists_0_70}
\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5Hhists0_06_5.png}
    \caption{$s_c = 0.06$. Note that it is difficult to reach
    tCE2.}\label{fig:Hhists_0_06}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5Hhists0_20_5.png}
    \caption{$s_c = 0.2$. Note that tCE2 is both reached with substantial
    probability and has substantial obliquity.}\label{fig:Hhists_0_20}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5Hhists0_60_5.png}
    \caption{$s_c = 0.6$. Note that tCE2 becomes attracting over tCE1, but will
    have obliquity $\approx I$ and is uninteresting.}\label{fig:Hhists_0_70}
\end{figure}

@@

Assuming that $\hat{s}$ is drawn from an isotropic distribution, we may then
calculate the probabilities of going to either tCE as a function of $s_c$. This
is shown below for $I = 5^\circ$
\begin{figure}
    \centering
    \includegraphics[width=0.6\textwidth]{../initial/1_weaktide/5probs_5.png}
    \caption{Top: total probability of ending up in tCE2 (blue dots) and the
    prediction ignoring separatrix capture (red line). Bottom:
    obliquities of the tCEs.}\label{fig:probs}
\end{figure}

Note that while only the results for an isotropic distribution of initial
$\hat{s}$ are shown, in principle arbitrary distributions $P\p{\theta_i}$ can be
convolved against the $P_{tCE2}\p{\theta_i}$ distributions shown in
\autoref{ss:q_dist}.
